Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
put caption in top

\begin{table}
\begin{center}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\cite{olivetti2013wonder} OE & 17 & compression distance, random forests \\
\cite{elizalde2013vector} ELF & 55 & i-vector, LDA \\
\cite{krijnders2013tone} KH & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} PE & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} NHL & 60 & unsupervised learning over Mel spectra, SVMs \\
\cite{nogueira2013sound} NR1 & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} CHR & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} GSR & 69 & Mel-frequency Spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} RG & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} LTT & 72 & MFCCs, tree baggers \\
\cite{roma2013recurrence} RNH & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84/87 & label tree embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & amplitude modulated spectra, LDA \\
\end{tabular}
\end{center}
\caption{Algorithms evaluated on the DCASE2013 ASC DCASE2013 dataset. RQA stands for recurrence quantification analysis and ILD for inter-aural differences. Algorithms above the horizontal line participated to the DCASE challenge. Others used the datasets afterward and the last used only the public dataset ($^*$).  \label{tab:dcase}}
\end{table}

@@

MFCCs are computed for windows of $50\,\mathrm{ms}$ and hops of $25\,\mathrm{ms}$, with full frequency range. Different ranks of coefficients were tested to compute the MFCCs, results here are only reported for the best setting, which consisted of $40$ MFCCs, including the first coefficient related to the average energy. This setting gives us $600$ feature vectors per scene. To get a more robust representation of lower dimensionality a pooling step is performed on the MFCCs: each recording is divided into $n$ non-overlapping $t$-seconds long ``texture'' windows. The MFCC vectors within each texture window are then averaged in time. As the \emph{ob} approaches involve a clustering step, we need to ensure that both MFCCs and scattering coefficients have a comparable number of vectors per recording. \ja{Why do we need to do this?} Thus, $t$ is set to $250\,\mathrm{ms}$, resulting in $120$ MFCCs texture windows per scene.

\ja{We've tested the impact of the logarithm here, but not of the feature selection or standardization. Should we do this as well? For the feature selection, we did say earlier that we would test its impact.}

@@

For ASSR, evaluation is performed on the private part of the DCASE2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. The $p@k$ is computed for $k=\{1,\ldots,9\}$, since each class only has $10$ items \ja{?}. Note that a $p@1$ is equivalent to the classification accuracy obtained by choosing the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approaches and the scaling parameter $N$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$. \ja{I'm not sure what this means. Do we fix $m$ and $N$ here for all experiments or do we optimize them over the test data each time? If so, this will bias the results, no?}

@@

For the MFCCs, there is no clear evidence that the \emph{ob} approaches improve the results. \ja{Why?}

@@

\begin{table}
\begin{center}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
early, linear  & $54\pm20$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
early, RBF     & $47\pm16$  & $56\pm\phantom{0}7$  & $63\pm\phantom{0}6$   \\
late, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
late, RBF     & $68\pm10$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\caption{Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.}
\end{center}
\label{table:dcase2013}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{lcc}
Features & MFCCs & log-scattering \\
Classifier  & GMMs    & linear SVMs \\
Temporal integration & late (product rule) & late (majority voting) \\
\midrule
beach & $74.6 \pm 18.9$ & $83.5 \pm \phantom{0}7.1$ \\
bus & $58.2 \pm 18.3$ & $88.8 \pm 11.4$ \\
caf\'{e} / restaurant & $85.1 \pm 10.8$ & $64.5 \pm \phantom{0}8.3$ \\
car & $69.1 \pm 20.8$ & $94.9 \pm \phantom{0}6.1$ \\
city center & $89.6 \pm \phantom{0}9.2$ & $91.7 \pm \phantom{0}9.4$ \\
forest path & $72.4 \pm 23.8$ & $93.8 \pm \phantom{0}7.8$ \\
grocery store & $74.1 \pm 13.7$ & $90.9 \pm \phantom{0}6.9$ \\
home & $78.1 \pm 17.7$ & $56.2 \pm 23.9$ \\
library & $65.1 \pm 23.3$ & $82.0 \pm 13.0$ \\
metro station & $85.2 \pm 15.6$ & $96.0 \pm \phantom{0}2.3$ \\
office & $90.8 \pm 16.0$ & $87.5 \pm 21.7$ \\
park & $25.6 \pm 11.0$ & $75.4 \pm \phantom{0}7.4$ \\
residential area & $75.1 \pm 19.4$ & $44.2 \pm 15.0$ \\
train & $34.1 \pm \phantom{0}7.2$ & $58.3 \pm 10.0$ \\
tram & $85.4 \pm 13.9$ & $83.7 \pm 12.2$ \\
\bottomrule
Average & $70.8 \pm \phantom{0}2.6$ & $79.4 \pm \phantom{0}3.0$
\end{tabular}
\end{center}
\label{table:dcase2016}
\caption{Class-wise accuracies on the DCASE 2016 dataset for two pipelines: a baseline of mel-frequency cepstral coefficients (MFCCs), Gaussian mixture models (GMMs), and late temporal integration by product of likelihoods ; and our proposed algorithm of log-scattering coefficients, support vector machines (SVMs) with a linear kernel, and late temporal integration by majority voting.}
\end{table}

>>>>

\begin{table}
\begin{center}
\caption{Algorithms evaluated on the DCASE2013 ASC DCASE2013 dataset. RQA stands for recurrence quantification analysis and ILD for inter-aural differences. Algorithms above the horizontal line participated to the DCASE challenge. Others used the datasets afterward and the last used only the public dataset ($^*$).  \label{tab:dcase}}
\begin{tabular}{lcl}
& Acc. \%  &  \multicolumn{1}{c}{Design}  \\
\cite{olivetti2013wonder} OE & 17 & compression distance, random forests \\
\cite{elizalde2013vector} ELF & 55 & i-vector, LDA \\
\cite{krijnders2013tone} KH & 55 & cochleogram, SVMs \\
\cite{patil2013multiresolution} PE & 58 & 2D Gabor filters, SVMs \\
\cite{lee2013acoustic} NHL & 60 & unsupervised learning over Mel spectra, SVMs \\
\cite{nogueira2013sound} NR1 & 60 & MFCCs and ILD features, SVMs \\
\cite{chum2013ieee} CHR & 65 & sparsity features, HMMs  \\
\cite{geiger2013large} GSR & 69 & Mel-frequency Spectra and MFCCs, SVMs \\
\cite{rakotomamonjy2015histogram} RG & 69 & histogram of gradient (HOG), SVMs \\
\cite{li2013auditory} LTT & 72 & MFCCs, tree baggers \\
\cite{roma2013recurrence} RNH & 76 & RQA features stacked with MFCCs, SVMs \\
\hline
\cite{phan2016label} & 84/87 & label tree embedding of Gammatone, SVMs \\
\cite{7362846} & 85$^*$ & amplitude modulated spectra, LDA \\
\end{tabular}
\end{center}
\end{table}

@@

MFCCs are computed for windows of $50\,\mathrm{ms}$ and hops of $25\,\mathrm{ms}$, with full frequency range. Different ranks of coefficients were tested to compute the MFCCs, results here are only reported for the best setting, which consisted of $40$ MFCCs, including the first coefficient related to the average energy. This setting gives us $600$ feature vectors per scene. To get a more robust representation of lower dimensionality a pooling step is performed on the MFCCs: each recording is divided into $n$ non-overlapping 250 seconds long ``texture'' windows \cite{1021072}, achieved a comparable number of vectors than while using the scattering ones.

%. The MFCC vectors within each texture window are then averaged in time. As the \emph{ob} approaches involve a clustering step, we need to ensure that both MFCCs and scattering coefficients have a comparable number of vectors per recording. Thus, $t$ is set to $250\,\mathrm{ms}$, resulting in $120$ MFCCs texture windows per scene.

%\ja{We've tested the impact of the logarithm here, but not of the feature selection or standardization. Should we do this as well? For the feature selection, we did say earlier that we would test its impact.}

@@

For ASSR, evaluation is performed on the private part of the DCASE2013 dataset. The metric used is the precision at rank $k$ ($p@k$), which is computed by taking a query item and counting the number of items of the same class within the $k$ closest neighbors, and then averaging over all query items. The $p@k$ is computed for $k=\{1,\ldots,9\}$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by choosing the label of the closest neighbor for a given item. For each experimental setting, we only report the results obtained with the sets of parameters, \emph{i.e.} the number of clusters $m$ for the \emph{ob} approaches and the scaling parameter $N$ of the RBF kernels (see Eq. \ref{eq:kc}) leading to the best $p@9$.

%\ja{I'm not sure what this means. Do we fix $m$ and $N$ here for all experiments or do we optimize them over the test data each time? If so, this will bias the results, no?}

@@

%For the MFCCs, there is no clear evidence that the \emph{ob} approaches improve the results. \ja{Why?}

@@

\begin{table}
\begin{center}
\caption{Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
early, linear  & $54\pm20$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
early, RBF     & $47\pm16$  & $56\pm\phantom{0}7$  & $63\pm\phantom{0}6$   \\
late, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
late, RBF     & $68\pm10$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\end{center}
\label{table:dcase2013}
\end{table}

@@

\begin{table}
\begin{center}
\caption{Class-wise accuracies on the DCASE 2016 dataset for two pipelines: a baseline of mel-frequency cepstral coefficients (MFCCs), Gaussian mixture models (GMMs), and late temporal integration by product of likelihoods ; and our proposed algorithm of log-scattering coefficients, support vector machines (SVMs) with a linear kernel, and late temporal integration by majority voting.}
\begin{tabular}{lcc}
Features & MFCCs & log-scattering \\
Classifier  & GMMs    & linear SVMs \\
Temporal integration & late (product rule) & late (majority voting) \\
\midrule
beach & $74.6 \pm 18.9$ & $83.5 \pm \phantom{0}7.1$ \\
bus & $58.2 \pm 18.3$ & $88.8 \pm 11.4$ \\
caf\'{e} / restaurant & $85.1 \pm 10.8$ & $64.5 \pm \phantom{0}8.3$ \\
car & $69.1 \pm 20.8$ & $94.9 \pm \phantom{0}6.1$ \\
city center & $89.6 \pm \phantom{0}9.2$ & $91.7 \pm \phantom{0}9.4$ \\
forest path & $72.4 \pm 23.8$ & $93.8 \pm \phantom{0}7.8$ \\
grocery store & $74.1 \pm 13.7$ & $90.9 \pm \phantom{0}6.9$ \\
home & $78.1 \pm 17.7$ & $56.2 \pm 23.9$ \\
library & $65.1 \pm 23.3$ & $82.0 \pm 13.0$ \\
metro station & $85.2 \pm 15.6$ & $96.0 \pm \phantom{0}2.3$ \\
office & $90.8 \pm 16.0$ & $87.5 \pm 21.7$ \\
park & $25.6 \pm 11.0$ & $75.4 \pm \phantom{0}7.4$ \\
residential area & $75.1 \pm 19.4$ & $44.2 \pm 15.0$ \\
train & $34.1 \pm \phantom{0}7.2$ & $58.3 \pm 10.0$ \\
tram & $85.4 \pm 13.9$ & $83.7 \pm 12.2$ \\
\bottomrule
Average & $70.8 \pm \phantom{0}2.6$ & $79.4 \pm \phantom{0}3.0$
\end{tabular}
\end{center}
\label{table:dcase2016}
\end{table}
